Competing Bandits: \\ The Perils of Exploration under Competition

### 2019-02-14 paper/content/model.tex
Minor edits in prelims.

Before the game starts, each firm commits to an MAB algorithm, and uses this algorithm to choose its actions. Each algorithm receives a ``warm start": additional $T_0$ agents that arrive before the game starts, and interact with the firm as described above. \gaedit{The warm start serves to vary the initial information the firm has before beginning to compete for users as well as to initialize the agents' perception of the firms.} Each firm's objective is to maximize its market share: the fraction of users who chose this firm.

@@

\xhdr{Agents.}
\gaedit{For simplicity we suppose that firms compete for agents on a single dimension, quality, that is summarized via the rewards experienced by past consumers.
\OMIT{\footnote{One can think that there are two quality types - a reward of 1 is a high type and a reward of 0 is a low type}}}
Agents are myopic and non-strategic: they \asedit{would like} to choose among the firms so as to maximize their expected reward \gaedit{(i.e. select the firm with the highest quality)}, without attempting to influence the firms' learning algorithms or rewards of the future users. Agents are not well-informed: they only receive a rough signal about each firm's performance before they choose a firm, and no other information.

Concretely, each of the two firms has a \emph{reputation score}, and each agent's choice is driven by these two numbers. We posit a version of rational behavior: each agent chooses a firm with a maximal reputation score (breaking ties uniformly). The reputation score is simply a sliding window average: an average reward of the last $M$ agents that chose this firm. \asedit{This is similar to ratings aggregators on many online platforms such as Yelp, Tripadvisor, etc.}

>>>>

Before the game starts, each firm commits to an MAB algorithm, and uses this algorithm to choose its actions. Each algorithm receives a ``warm start": additional $T_0$ agents that arrive before the game starts, and interact with the firm as described above. \asedit{The warm ensures that each firm has a meaningful reputation when competition starts.} Each firm's objective is to maximize its market share: the fraction of users who chose this firm.

@@

\xhdr{Agents.}
\asedit{Firms compete on a single dimension, quality of service, as expressed by agents' rewards.}
\OMIT{\footnote{One can think that there are two quality types - a reward of 1 is a high type and a reward of 0 is a low type}}
Agents are myopic and non-strategic: they \asedit{would like} to choose among the firms so as to maximize their expected reward \gaedit{(i.e. select the firm with the highest quality)}, without attempting to influence the firms' learning algorithms or rewards of the future users. Agents are not well-informed: they only receive a rough signal about each firm's performance before they choose a firm, and no other information.

Concretely, each of the two firms has a \emph{reputation score}, and each agent's choice is driven by these two numbers. We posit a version of rational behavior: each agent chooses a firm with a maximal reputation score (breaking ties uniformly). The reputation score is simply a sliding window average: an average reward of the last $M$ agents that chose this firm.

%\asedit{This is similar to ratings aggregators on many online platforms such as Yelp, Tripadvisor, etc.}
